%-------------------------
% Resume in LaTeX
% Author : Felix Hernandez Vieyra
% Based on: Sourabh Bajaj's template
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/Felix-Hz}{\Large Felix Hernandez Vieyra}} & Visa: NZ Open Work Until 2028 \\
   \href{https://www.credly.com/badges/9cacb43b-eb02-45df-bb40-1176c09ea7f2/linked_in_profile}{Software Engineer | AWS Cloud Certified} & Email: \href{mailto:felix.hzv@gmail.com}{felix.hzv@gmail.com}\\
  \href{https://www.felix-hzv.dev}{felix-hzv.dev} & Mobile: \href{tel:+6421925790}{+64 21 925 790} \\
  \href{https://github.com/Felix-Hz}{github.com/Felix-Hz} & Auckland, New Zealand \\
\end{tabular*}

%-----------SUMMARY-----------------
\vspace{6pt}
\small{
I thrive in environments where I can take on diverse responsibilities and deliver on high-pressure deadlines with strong customer focus. Continuously learning new technologies and dedicated to building extensible, performant, and resilient software. Outside of work, I'm a social person and music enthusiast who enjoys flying drones and learning Dutch.
}

%-----------SKILLS-----------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Programming Languages}{: Python, TypeScript, Golang, C\#}
    }
    \vspace{-5pt}
    \item{
      \textbf{Databases}{: PostgreSQL, MySQL, SQLite, DynamoDB}
    }
    \vspace{-5pt}
    \item{
      \textbf{Frameworks \& Tools}{: Flask, FastAPI, Pydantic, Node.js, Express.js, React, Vue, Remix, Next.js, .NET}
    }
    \vspace{-5pt}
    \item{
      \textbf{Cloud \& DevOps}{: AWS, Linux, Docker, CI/CD, Infrastructure-as-Code (Terraform, CDK, CloudFormation), Git}
    }
    \vspace{-5pt}
    \item{
      \textbf{Data Engineering}{: Databricks, ETL pipelines, Data Wrangling, Analysis \& Visualization}
    }
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Infinity Studio}{Auckland, New Zealand}
      {Intermediate Software Engineer}{April 2024 -- Dec 2025 (1.5+ years)}
      \resumeItemListStart
        \resumeItem{Company Context}
          {Geotechnical engineering platform enabling field data collection, infrastructure design workflows, liquefaction risk analysis, and parameter correlations for engineering teams.}
        \resumeItem{Product Development}
          {Built and maintained 50+ end-to-end features and Python-based platform services to support geotechnical engineers, improving operational efficiency and data accuracy.}
        \resumeItem{RESTful API Development}
          {Designed and implemented multiple RESTful APIs to perform complex analyses, export data, and generate custom PDF reports, enabling seamless integration with client workflows.}
        \resumeItem{Domain Modeling}
          {Modeled geotechnical engineering domain problems into well-structured, maintainable software solutions, collaborating closely with subject matter experts to ensure technical accuracy.}
        \resumeItem{Front-End Development}
          {Built high-performance, pixel-perfect, and secure front-end layouts using modern JavaScript frameworks, enhancing user experience and interface responsiveness.}
        \resumeItem{Testing \& Quality}
          {Implemented comprehensive unit and integration tests to enhance code quality, reliability, and maintainability across the platform.}
        \resumeItem{Infrastructure-as-Code}
          {Developed infrastructure-as-code solutions for robust, automated, and scalable cloud environment deployments, reducing deployment time and infrastructure drift.}
      \resumeItemListEnd

    \resumeSubheading
      {Decodata}{Amsterdam, The Netherlands}
      {Full-Stack Software Engineer}{July 2023 -- February 2024 (8 months)}
      \resumeItemListStart
        \resumeItem{Company Context}
          {Furniture industry data management platform enabling product catalog automation, design asset processing, and supplier integrations.}
        \resumeItem{Data Processing}
          {Built back-end systems to manage and transform large volumes of design and product data, including pattern matching with regular expressions and image processing pipelines.}
        \resumeItem{User Interface Design}
          {Built intuitive user interfaces that balanced design, performance, security, and responsive behavior across devices, improving user engagement and satisfaction.}
        \resumeItem{Cloud Infrastructure}
          {Built and maintained cloud infrastructure-as-code with best practices, enabling efficient deployment, monitoring, and resilience of production systems.}
      \resumeItemListEnd

    \resumeSubheading
      {FeedProfessionals Ltda.}{Buenos Aires, Argentina}
      {Junior Python Developer}{January 2023 -- July 2023 (7 months)}
      \resumeItemListStart
        \resumeItem{Data Pipeline Automation}
          {Automated the customs data pipeline, improving report delivery time by 75\% through analysis of datasets covering 5+ products from multiple countries across South America over 10+ years.}
        \resumeItem{Data Gathering}
          {Implemented efficient data collection and processing workflows to support business intelligence and reporting needs.}
      \resumeItemListEnd

    \resumeSubheading
      {University of Calgary}{Calgary, Canada}
      {ELAP Scholarship Holder (Student Exchange)}{June 2022 -- December 2022 (6 months)}
      \resumeItemListStart
        \resumeItem{Research Collaboration}
          {Collaborated with a research team on publishing an article in a leading academic journal, contributing to neuroscience research methodologies.}
        \resumeItem{Academic Excellence}
          {Secured scholarship in recognition of academic excellence, covering tuition, mobility expenses, and stay in Canada.}
      \resumeItemListEnd

    \resumeSubheading
      {Cognitive Neuroscience Laboratory (UdeSA)}{Buenos Aires, Argentina}
      {Research Assistant (Internship)}{March 2022 -- June 2022 (6 months)}
      \resumeItemListStart
        \resumeItem{Machine Learning Research}
          {Documented and reviewed Python code in a machine learning (NLP) clinical project for early detection of dementia, contributing to research methodologies and reproducibility.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University del Salvador}{Buenos Aires, Argentina}
      {Bachelor of Science in Psychology; GPA: 9.17/10.0 (Top 5\% of degree)}{March 2019 -- December 2022}
      \resumeItemListStart
        \resumeItem{Research Excellence}
          {Discontinued after 4 years out of 5 to pursue career transition. Intensively participated in a Cognitive Neuroscience research lab, gaining strong analytical and research skills.}
        \resumeItem{Self-Directed Learning}
          {Highly motivated to learn computer science, enrolled in multiple data science and software development courses alongside degree studies.}
        \resumeItem{Specialized Coursework}
          {Completed university courses in Data Structures \& Algorithms, Programming, and Operative Systems, building strong foundations in computer science.}
      \resumeItemListEnd

    \resumeSubheading
      {University of Calgary}{Calgary, Canada}
      {Exchange Student, Cognitive Science (ELAP Scholarship Holder)}{August 2022 -- January 2023}
      \resumeItemListStart
        \resumeItem{Academic Focus}
          {Completed coursework in Statistics \& Research Methods, Neuroscience, and Psychometry, utilizing IBM SPSS for statistical data analysis.}
        \resumeItem{Career Catalyst}
          {Academic experience reinforced commitment to pursuing software engineering, bridging cognitive science with technical problem-solving approaches.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------ADDITIONAL EDUCATION-----------------
\section{Professional Development}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Le Wagon}{Amsterdam, The Netherlands}
      {Data Engineering Course (360 hours)}{Completed}
      \resumeItemListStart
        \resumeItem{Curriculum}
          {Intensive Python-based curriculum focused on modern data workflows, including data preparation, ETL automation, visualization, and machine learning pipelines.}
      \resumeItemListEnd

    \resumeSubheading
      {Digital House}{Buenos Aires, Argentina}
      {Web Development}{August 2021 -- February 2022}
      \resumeItemListStart
        \resumeItem{Front-End Development}
          {Enhanced proficiency in wireframing, layout design, styling, animation, and DOM manipulation using modern JavaScript frameworks for responsive, mobile-first, single-page applications.}
        \resumeItem{Back-End Development}
          {Developed expertise in relational database management, server-side programming, and RESTful API integration following agile methodologies and coding best practices.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------------
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeSubItem{AWS Certified Cloud Practitioner}
      {Amazon Web Services (December 2023 -- Expires December 2026)}
    \resumeSubItem{AWS Solutions Architect Associate (WIP)}
      {Amazon Web Services (November 2025 -- Present, In Progress)}
  \resumeSubHeadingListEnd

%-----------LANGUAGES-----------------
\section{Languages}
  \resumeSubHeadingListStart
    \resumeSubItem{English}
      {IB English as Second Language -- Full Professional Proficiency}
    \resumeSubItem{Spanish}
      {Native level}
    \resumeSubItem{French/Portuguese/Dutch}
      {Basic conversational level}
  \resumeSubHeadingListEnd

%-----------AWARDS-----------------
\section{Awards \& Congress}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://www.educanada.ca/scholarships-bourses/can/institutions/elap-pfla.aspx?lang=eng}{Emerging Leaders in the Americas}}
      {Secured scholarship in recognition of academic excellence, covering tuition, mobility expenses, and stay in Canada (June 2022 -- December 2022)}
    \resumeSubItem{\href{https://ji.psi.uba.ar/xxviii/esp/index.php?idtaller=553}{XIII International Research and Practice in Psychology Congress}}
      {Delivered a workshop on Programming in R for Researchers at Universidad de Buenos Aires}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
